Unicode Implementation Issues \thanks { This is a working document for the Rexx Language Association (RexxLA). There will be one or more separate requirements documents. It is written in \LaTeX\ \fmtversion\ and was rendered \today\ using \enginedetails. }

### 2024-02-16 ARB/standards/work-in-progress/document/tex/standard/provided_classes.tex
work in standard book production process including readme.md
upd

\hypertarget{provided-classes}{%
\chapter{Provided classes}\label{provided-classes}}

@@

\hypertarget{collection-class-routines}{%
\subsection{Collection Class Routines}\label{collection-class-routines}}

@@

\hypertarget{the-collection-class}{%
\subsection{The collection class}\label{the-collection-class}}

@@

\hypertarget{init}{%
\subsubsection{INIT}\label{init}}

@@

\hypertarget{exposed}{%
\subsubsection{EXPOSED}\label{exposed}}

@@

\hypertarget{findindex}{%
\subsubsection{FINDINDEX}\label{findindex}}

@@

\hypertarget{at}{%
\subsubsection{AT}\label{at}}

@@

\hypertarget{section}{%
\subsubsection{{[}{]}}\label{section}}

@@

\hypertarget{put}{%
\subsubsection{PUT}\label{put}}

@@

\hypertarget{section-1}{%
\subsubsection{{[}{]}=}\label{section-1}}

@@

\hypertarget{hasindex}{%
\subsubsection{HASINDEX}\label{hasindex}}

@@

\hypertarget{items}{%
\subsubsection{ITEMS}\label{items}}

@@

\hypertarget{remove}{%
\subsubsection{REMOVE}\label{remove}}

@@

\hypertarget{removeit}{%
\subsubsection{REMOVEIT}\label{removeit}}

@@

\hypertarget{makearrya}{%
\subsubsection{MAKEARRYA}\label{makearrya}}

@@

\hypertarget{makearrayx}{%
\subsubsection{MAKEARRAYX}\label{makearrayx}}

@@

\hypertarget{supplier}{%
\subsubsection{SUPPLIER}\label{supplier}}

@@

\hypertarget{class-list}{%
\subsection{Class list}\label{class-list}}

@@

\hypertarget{put-1}{%
\subsubsection{PUT}\label{put-1}}

@@

\hypertarget{of}{%
\subsubsection{OF}\label{of}}

@@

\hypertarget{insert}{%
\subsubsection{INSERT}\label{insert}}

@@

\hypertarget{first}{%
\subsubsection{FIRST}\label{first}}

@@

\hypertarget{last}{%
\subsubsection{LAST}\label{last}}

@@

\hypertarget{firstitem}{%
\subsubsection{FIRSTITEM}\label{firstitem}}

@@

\hypertarget{lastitem}{%
\subsubsection{LASTITEM}\label{lastitem}}

@@

\hypertarget{next}{%
\subsubsection{NEXT}\label{next}}

@@

\hypertarget{previous}{%
\subsubsection{PREVIOUS}\label{previous}}

@@

\hypertarget{section-2}{%
\subsubsection{SECTION}\label{section-2}}

@@

\hypertarget{class-queue}{%
\subsection{Class queue}\label{class-queue}}

@@

\hypertarget{push}{%
\subsubsection{PUSH}\label{push}}

@@

\hypertarget{queue}{%
\subsubsection{QUEUE}\label{queue}}

@@

\hypertarget{peek}{%
\subsubsection{PEEK}\label{peek}}

@@

\hypertarget{remove-1}{%
\subsubsection{REMOVE}\label{remove-1}}

@@

\hypertarget{class-table}{%
\subsection{Class table}\label{class-table}}

@@

\hypertarget{makearray}{%
\subsubsection{MAKEARRAY}\label{makearray}}

@@

\hypertarget{union}{%
\subsubsection{UNION}\label{union}}

@@

\hypertarget{intersection}{%
\subsubsection{INTERSECTION}\label{intersection}}

@@

\hypertarget{xor}{%
\subsubsection{XOR}\label{xor}}

@@

\hypertarget{difference}{%
\subsubsection{DIFFERENCE}\label{difference}}

@@

\hypertarget{subset}{%
\subsubsection{SUBSET}\label{subset}}

@@

\hypertarget{class-set}{%
\subsubsection{Class set}\label{class-set}}

@@

\hypertarget{put-2}{%
\subsubsection{PUT}\label{put-2}}

@@

\hypertarget{of-1}{%
\subsubsection{OF}\label{of-1}}

@@

\hypertarget{union-1}{%
\subsubsection{UNION}\label{union-1}}

@@

\hypertarget{intersection-1}{%
\subsubsection{INTERSECTION}\label{intersection-1}}

@@

\hypertarget{xor-1}{%
\subsubsection{XOR}\label{xor-1}}

@@

\hypertarget{difference-1}{%
\subsubsection{DIFFERENCE}\label{difference-1}}

@@

\hypertarget{class-relation}{%
\subsection{Class relation}\label{class-relation}}

@@

\hypertarget{put-3}{%
\subsubsection{PUT}\label{put-3}}

@@

\hypertarget{items-1}{%
\subsubsection{ITEMS}\label{items-1}}

@@

\hypertarget{makearray-1}{%
\subsubsection{MAKEARRAY}\label{makearray-1}}

@@

\hypertarget{supplier-1}{%
\subsubsection{SUPPLIER}\label{supplier-1}}

@@

\hypertarget{intersection-2}{%
\subsubsection{INTERSECTION}\label{intersection-2}}

@@

\hypertarget{xor-2}{%
\subsubsection{XOR}\label{xor-2}}

@@

\hypertarget{difference-2}{%
\subsubsection{DIFFERENCE}\label{difference-2}}

@@

\hypertarget{subset-1}{%
\subsubsection{SUBSET}\label{subset-1}}

@@

\hypertarget{removeitem}{%
\subsubsection{REMOVEITEM}\label{removeitem}}

@@

\hypertarget{index}{%
\subsubsection{INDEX}\label{index}}

@@

\hypertarget{allat}{%
\subsubsection{ALLAT}\label{allat}}

@@

\hypertarget{hasitem}{%
\subsubsection{HASITEM}\label{hasitem}}

@@

\hypertarget{allindex}{%
\subsubsection{ALLINDEX}\label{allindex}}

@@

\hypertarget{of-2}{%
\subsubsection{OF}\label{of-2}}

@@

\hypertarget{put-4}{%
\subsubsection{PUT}\label{put-4}}

@@

\hypertarget{union-2}{%
\subsubsection{UNION}\label{union-2}}

@@

\hypertarget{intersection-3}{%
\subsubsection{INTERSECTION}\label{intersection-3}}

@@

\hypertarget{xor-3}{%
\subsubsection{XOR}\label{xor-3}}

@@

\hypertarget{difference-3}{%
\subsubsection{DIFFERENCE}\label{difference-3}}

@@

\hypertarget{the-directory-class}{%
\subsection{The directory class}\label{the-directory-class}}

@@

\hypertarget{at-1}{%
\subsubsection{AT}\label{at-1}}

@@

\hypertarget{put-5}{%
\subsubsection{PUT}\label{put-5}}

@@

\hypertarget{makearray-2}{%
\subsubsection{MAKEARRAY}\label{makearray-2}}

@@

\hypertarget{supplier-2}{%
\subsubsection{SUPPLIER}\label{supplier-2}}

@@

\hypertarget{intersection-4}{%
\subsubsection{INTERSECTION}\label{intersection-4}}

@@

\hypertarget{xor-4}{%
\subsubsection{XOR}\label{xor-4}}

@@

\hypertarget{difference-4}{%
\subsubsection{DIFFERENCE}\label{difference-4}}

@@

\hypertarget{subset-2}{%
\subsubsection{SUBSET}\label{subset-2}}

@@

\hypertarget{setentry}{%
\subsubsection{SETENTRY}\label{setentry}}

@@

\hypertarget{entry}{%
\subsubsection{ENTRY}\label{entry}}

@@

\hypertarget{hasentry}{%
\subsubsection{HASENTRY}\label{hasentry}}

@@

\hypertarget{setmethod}{%
\subsubsection{SETMETHOD}\label{setmethod}}

@@

\hypertarget{unknown}{%
\subsubsection{UNKNOWN}\label{unknown}}

@@

\hypertarget{the-stream-class}{%
\section{The stream class}\label{the-stream-class}}

@@

\hypertarget{the-alarm-class}{%
\section{The alarm class}\label{the-alarm-class}}

@@

\hypertarget{the-monitor-class}{%
\section{The monitor class}\label{the-monitor-class}}

@@

\hypertarget{init-1}{%
\subsection{INIT}\label{init-1}}

@@

\hypertarget{current}{%
\subsection{CURRENT}\label{current}}

@@

\hypertarget{destination}{%
\subsection{DESTINATION}\label{destination}}

@@

\hypertarget{unknown-1}{%
\subsection{UNKNOWN}\label{unknown-1}}

>>>>

%preprocessed texin
\chapter{Provided classes}\label{provided-classes}

@@

\subsection{Collection Class Routines}\label{collection-class-routines}

@@

\subsection{The collection class}\label{the-collection-class}

@@

\subsubsection{INIT}\label{init}

@@

\subsubsection{EXPOSED}\label{exposed}

@@

\subsubsection{FINDINDEX}\label{findindex}

@@

\subsubsection{AT}\label{at}

@@

\subsubsection{{[}{]}}\label{section}

@@

\subsubsection{PUT}\label{put}

@@

\subsubsection{{[}{]}=}\label{section-1}

@@

\subsubsection{HASINDEX}\label{hasindex}

@@

\subsubsection{ITEMS}\label{items}

@@

\subsubsection{REMOVE}\label{remove}

@@

\subsubsection{REMOVEIT}\label{removeit}

@@

\subsubsection{MAKEARRYA}\label{makearrya}

@@

\subsubsection{MAKEARRAYX}\label{makearrayx}

@@

\subsubsection{SUPPLIER}\label{supplier}

@@

\subsection{Class list}\label{class-list}

@@

\subsubsection{PUT}\label{put-1}

@@

\subsubsection{OF}\label{of}

@@

\subsubsection{INSERT}\label{insert}

@@

\subsubsection{FIRST}\label{first}

@@

\subsubsection{LAST}\label{last}

@@

\subsubsection{FIRSTITEM}\label{firstitem}

@@

\subsubsection{LASTITEM}\label{lastitem}

@@

\subsubsection{NEXT}\label{next}

@@

\subsubsection{PREVIOUS}\label{previous}

@@

\subsubsection{SECTION}\label{section-2}

@@

\subsection{Class queue}\label{class-queue}

@@

\subsubsection{PUSH}\label{push}

@@

\subsubsection{QUEUE}\label{queue}

@@

\subsubsection{PEEK}\label{peek}

@@

\subsubsection{REMOVE}\label{remove-1}

@@

\subsection{Class table}\label{class-table}

@@

\subsubsection{MAKEARRAY}\label{makearray}

@@

\subsubsection{UNION}\label{union}

@@

\subsubsection{INTERSECTION}\label{intersection}

@@

\subsubsection{XOR}\label{xor}

@@

\subsubsection{DIFFERENCE}\label{difference}

@@

\subsubsection{SUBSET}\label{subset}

@@

\subsubsection{Class set}\label{class-set}

@@

\subsubsection{PUT}\label{put-2}

@@

\subsubsection{OF}\label{of-1}

@@

\subsubsection{UNION}\label{union-1}

@@

\subsubsection{INTERSECTION}\label{intersection-1}

@@

\subsubsection{XOR}\label{xor-1}

@@

\subsubsection{DIFFERENCE}\label{difference-1}

@@

\subsection{Class relation}\label{class-relation}

@@

\subsubsection{PUT}\label{put-3}

@@

\subsubsection{ITEMS}\label{items-1}

@@

\subsubsection{MAKEARRAY}\label{makearray-1}

@@

\subsubsection{SUPPLIER}\label{supplier-1}

@@

\subsubsection{INTERSECTION}\label{intersection-2}

@@

\subsubsection{XOR}\label{xor-2}

@@

\subsubsection{DIFFERENCE}\label{difference-2}

@@

\subsubsection{SUBSET}\label{subset-1}

@@

\subsubsection{REMOVEITEM}\label{removeitem}

@@

\subsubsection{INDEX}\label{index}

@@

\subsubsection{ALLAT}\label{allat}

@@

\subsubsection{HASITEM}\label{hasitem}

@@

\subsubsection{ALLINDEX}\label{allindex}

@@

\subsubsection{OF}\label{of-2}

@@

\subsubsection{PUT}\label{put-4}

@@

\subsubsection{UNION}\label{union-2}

@@

\subsubsection{INTERSECTION}\label{intersection-3}

@@

\subsubsection{XOR}\label{xor-3}

@@

\subsubsection{DIFFERENCE}\label{difference-3}

@@

\subsection{The directory class}\label{the-directory-class}

@@

\subsubsection{AT}\label{at-1}

@@

\subsubsection{PUT}\label{put-5}

@@

\subsubsection{MAKEARRAY}\label{makearray-2}

@@

\subsubsection{SUPPLIER}\label{supplier-2}

@@

\subsubsection{INTERSECTION}\label{intersection-4}

@@

\subsubsection{XOR}\label{xor-4}

@@

\subsubsection{DIFFERENCE}\label{difference-4}

@@

\subsubsection{SUBSET}\label{subset-2}

@@

\subsubsection{SETENTRY}\label{setentry}

@@

\subsubsection{ENTRY}\label{entry}

@@

\subsubsection{HASENTRY}\label{hasentry}

@@

\subsubsection{SETMETHOD}\label{setmethod}

@@

\subsubsection{UNKNOWN}\label{unknown}

@@

\section{The stream class}\label{the-stream-class}

@@

\section{The alarm class}\label{the-alarm-class}

@@

\section{The monitor class}\label{the-monitor-class}

@@

\subsection{INIT}\label{init-1}

@@

\subsection{CURRENT}\label{current}

@@

\subsection{DESTINATION}\label{destination}

@@

\subsection{UNKNOWN}\label{unknown-1}

### 2024-02-16 ARB/standards/work-in-progress/document/tex/standard/syntax_constructs.tex
work in standard book production process including readme.md
upd

\hypertarget{syntax-constructs}{%
\chapter{Syntax constructs}\label{syntax-constructs}}

\hypertarget{notation}{%
\section{Notation}\label{notation}}

\hypertarget{backus-naur-form-bnf}{%
\subsection{Backus-Naur Form (BNF)}\label{backus-naur-form-bnf}}

@@

\hypertarget{operands}{%
\subsection{Operands}\label{operands}}

@@

\hypertarget{grouping}{%
\subsection{Grouping}\label{grouping}}

@@

\hypertarget{bnf-syntax-definition}{%
\subsection{BNF syntax definition}\label{bnf-syntax-definition}}

@@

\hypertarget{syntactic-errors}{%
\subsection{Syntactic errors}\label{syntactic-errors}}

@@

\hypertarget{lexical}{%
\section{Lexical}\label{lexical}}

@@

\hypertarget{lexical-elements}{%
\subsection{Lexical elements}\label{lexical-elements}}

\hypertarget{events}{%
\subsubsection{Events}\label{events}}

@@

\hypertarget{rules}{%
\subsubsection{Rules}\label{rules}}

@@

\hypertarget{lexical-level}{%
\subsection{Lexical level}\label{lexical-level}}

\hypertarget{interaction-between-levels-of-syntax}{%
\subsection{Interaction between levels of
syntax}\label{interaction-between-levels-of-syntax}}

@@

\hypertarget{reserved-symbols}{%
\subsubsection{Reserved symbols}\label{reserved-symbols}}

@@

\hypertarget{function-name-syntax}{%
\subsubsection{Function name syntax}\label{function-name-syntax}}

@@

\hypertarget{syntax}{%
\section{Syntax}\label{syntax}}

\hypertarget{syntax-elements}{%
\subsection{Syntax elements}\label{syntax-elements}}

@@

\hypertarget{syntax-level}{%
\subsection{Syntax level}\label{syntax-level}}

@@

\hypertarget{syntactic-information}{%
\section{Syntactic information}\label{syntactic-information}}

\hypertarget{var_symbol-matching}{%
\subsection{VAR\_SYMBOL matching}\label{var_symbol-matching}}

@@

\hypertarget{trace-only-labels}{%
\subsection{Trace-only labels}\label{trace-only-labels}}

@@

\hypertarget{clauses-and-line-numbers}{%
\subsection{Clauses and line numbers}\label{clauses-and-line-numbers}}

@@

\hypertarget{nested-if-instructions}{%
\subsection{Nested IF instructions}\label{nested-if-instructions}}

@@

\hypertarget{choice-of-messages}{%
\subsection{Choice of messages}\label{choice-of-messages}}

@@

\hypertarget{creation-of-messages}{%
\subsection{Creation of messages}\label{creation-of-messages}}

@@

\hypertarget{error-message-prefix}{%
\subsubsection{Error message prefix}\label{error-message-prefix}}

@@

\hypertarget{replacement-of-insertions}{%
\section{Replacement of insertions}\label{replacement-of-insertions}}

@@

\hypertarget{syntactic-equivalence}{%
\section{Syntactic equivalence}\label{syntactic-equivalence}}

>>>>

%preprocessed texin
\chapter{Syntax constructs}\label{syntax-constructs}

\section{Notation}\label{notation}

\subsection{Backus-Naur Form (BNF)}\label{backus-naur-form-bnf}

@@

\subsection{Operands}\label{operands}

@@

\subsection{Grouping}\label{grouping}

@@

\subsection{BNF syntax definition}\label{bnf-syntax-definition}

@@

\subsection{Syntactic errors}\label{syntactic-errors}

@@

\section{Lexical}\label{lexical}

@@

\subsection{Lexical elements}\label{lexical-elements}

\subsubsection{Events}\label{events}

@@

\subsubsection{Rules}\label{rules}

@@

\subsection{Lexical level}\label{lexical-level}

\subsection{Interaction between levels of
syntax}\label{interaction-between-levels-of-syntax}

@@

\subsubsection{Reserved symbols}\label{reserved-symbols}

@@

\subsubsection{Function name syntax}\label{function-name-syntax}

@@

\section{Syntax}\label{syntax}

\subsection{Syntax elements}\label{syntax-elements}

@@

\subsection{Syntax level}\label{syntax-level}

@@

\section{Syntactic information}\label{syntactic-information}

\subsection{VAR\_SYMBOL matching}\label{var_symbol-matching}

@@

\subsection{Trace-only labels}\label{trace-only-labels}

@@

\subsection{Clauses and line numbers}\label{clauses-and-line-numbers}

@@

\subsection{Nested IF instructions}\label{nested-if-instructions}

@@

\subsection{Choice of messages}\label{choice-of-messages}

@@

\subsection{Creation of messages}\label{creation-of-messages}

@@

\subsubsection{Error message prefix}\label{error-message-prefix}

@@

\section{Replacement of insertions}\label{replacement-of-insertions}

@@

\section{Syntactic equivalence}\label{syntactic-equivalence}
